% ============================================================
%  PriceIQ — Test Plan and Test Cases
%  BTech Final Year Project, 2025-2026
% ============================================================
\documentclass[12pt,a4paper]{report}

\usepackage[top=1in,bottom=1in,left=1.2in,right=1in]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{parskip}
\usepackage{setspace}
\usepackage{mdframed}
\usepackage{colortbl}

\definecolor{priblue}{RGB}{0,82,165}
\definecolor{lightblue}{RGB}{210,230,255}
\definecolor{passgreen}{RGB}{0,140,0}
\definecolor{failred}{RGB}{180,0,0}
\definecolor{pendyellow}{RGB}{200,140,0}
\definecolor{rowgray}{RGB}{248,248,248}
\definecolor{headerblue}{RGB}{220,235,255}
\definecolor{unitcol}{RGB}{220,240,255}
\definecolor{intcol}{RGB}{220,255,225}
\definecolor{syscol}{RGB}{255,245,210}
\definecolor{perfcol}{RGB}{255,225,225}
\definecolor{seccol}{RGB}{240,220,255}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\textit{PriceIQ --- Test Plan v1.0}}
\fancyhead[R]{\small\textit{BTech Final Year Project 2025--2026}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

\setlength{\parskip}{6pt}
\setlength{\parindent}{0pt}
\onehalfspacing

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}

\newmdenv[linecolor=priblue,backgroundcolor=lightblue!40,
          linewidth=1pt,skipabove=6pt,skipbelow=6pt]{notebox}

% Status colours
\newcommand{\PASS}{\textcolor{passgreen}{\textbf{PASS}}}
\newcommand{\FAIL}{\textcolor{failred}{\textbf{FAIL}}}
\newcommand{\PEND}{\textcolor{pendyellow}{\textbf{PLANNED}}}

\begin{document}

% ─── TITLE PAGE ─────────────────────────────────────────────────────────────
\begin{titlepage}
  \centering
  \vspace*{1.8cm}
  {\Huge\bfseries\color{priblue} PriceIQ\par}
  \vspace{0.4cm}
  {\large AI-Powered Electronics Price Comparison for Indian Consumers\par}
  \vspace{1.4cm}
  \rule{0.85\linewidth}{1.5pt}\\[0.5cm]
  {\LARGE\bfseries Test Plan and Test Cases\par}
  \vspace{0.3cm}
  {\large Document Version 1.0\par}
  \rule{0.85\linewidth}{1.5pt}
  \vspace{1.8cm}

  \begin{tabular}{@{}ll@{}}
    \textbf{Project Type:}    & BTech Final Year Project \\[4pt]
    \textbf{Department:}      & Computer Science and Engineering \\[4pt]
    \textbf{Academic Year:}   & 2025--2026 \\[4pt]
    \textbf{Prepared By:}     & Adrij Bhadra \\[4pt]
    \textbf{Date:}            & April 2026 \\[4pt]
    \textbf{Document Status:} & Final \\
  \end{tabular}

  \vfill
  {\small Covers: Unit Tests, Integration Tests, System / End-to-End Tests,\\
  Performance Tests, Security Tests, and Traceability Matrix.}
\end{titlepage}

\tableofcontents
\newpage

% ─── CHAPTER 1: INTRODUCTION ─────────────────────────────────────────────────
\chapter{Introduction}

\section{Purpose}
This Test Plan defines the testing strategy, test environment, and test cases
for the PriceIQ system. The document covers \textbf{56 test cases} across five
testing categories: Unit, Integration, System / End-to-End, Performance, and
Security. The primary goal is to verify that each functional requirement (FR)
defined in the SRS is correctly implemented and that the system meets its
non-functional requirements.

\section{Scope}
\textbf{In scope:}
\begin{itemize}[noitemsep]
  \item Unit tests for the \texttt{matcher.ts} scoring engine (pure functions).
  \item Unit tests for utility functions in scraper modules.
  \item Integration tests for all REST API endpoints.
  \item System tests for key user workflows (search, compare, AI analysis).
  \item Performance tests for response latency and load.
  \item Security tests for the authenticated scrape endpoint and input handling.
\end{itemize}

\textbf{Out of scope:}
\begin{itemize}[noitemsep]
  \item End-to-end browser tests requiring Playwright against a live deployment.
  \item Load tests simulating more than 10 concurrent users.
  \item Testing of the Groq API itself (third-party service).
\end{itemize}

\section{Testing Approach and Status}
\begin{notebox}
The PriceIQ codebase does not yet include an automated test suite. This
document specifies the full set of planned test cases, written from code
analysis. All cases are marked \PEND{} (Planned); they would be executed
using \textbf{Jest} (unit/integration) and \textbf{Playwright Test}
(system/E2E) once a test harness is configured. The product matching engine
(\texttt{matcher.ts}) uses pure functions with no I/O and is the highest
priority for automated testing.

TypeScript type correctness is enforced via the Next.js build pipeline
(\texttt{next build}) since the project does not have a standalone
\texttt{typescript} dev dependency; the build is confirmed green in the
project history.
\end{notebox}

\section{References}
\begin{itemize}[noitemsep]
  \item PriceIQ Software Requirements Specification v1.0 (\texttt{srs.tex})
  \item PriceIQ System Design Document v1.0 (\texttt{system\_design.tex})
  \item Source files: \texttt{src/lib/scrapers/matcher.ts},
        \texttt{src/lib/scrapers/live.ts},
        \texttt{src/app/api/search/live/route.ts}
\end{itemize}

% ─── CHAPTER 2: TEST STRATEGY ────────────────────────────────────────────────
\chapter{Test Strategy}

\section{Testing Types}

\begin{longtable}{L{2.5cm} L{3.5cm} L{7cm}}
  \toprule
  \textbf{Type} & \textbf{Tool} & \textbf{Description} \\
  \midrule
  \endhead
  Unit Testing &
    Jest + ts-jest &
    Tests individual pure functions in \texttt{matcher.ts} and utility
    modules in isolation. No network or database access. \\[3pt]
  Integration Testing &
    Jest + Supertest &
    Tests API route handlers against a test PostgreSQL database using
    real HTTP calls. Scrapers are mocked to return deterministic fixtures. \\[3pt]
  System / E2E Testing &
    Manual / Playwright Test &
    Tests complete user workflows in a running application instance. Validates
    UI rendering, navigation, and data accuracy end-to-end. \\[3pt]
  Performance Testing &
    Manual + \texttt{k6} &
    Measures response latency and throughput for critical paths under
    realistic load conditions. \\[3pt]
  Security Testing &
    Manual + OWASP ZAP &
    Verifies authentication on protected endpoints, input validation,
    and absence of sensitive data leakage. \\
  \bottomrule
\end{longtable}

\section{Entry and Exit Criteria}

\begin{longtable}{L{2.5cm} L{5.5cm} L{5cm}}
  \toprule
  \textbf{Phase} & \textbf{Entry Criteria} & \textbf{Exit Criteria} \\
  \midrule
  \endhead
  Unit Testing &
    \texttt{matcher.ts} source compiles with zero TypeScript errors. &
    All 27 unit test cases pass with zero failures. \\[3pt]
  Integration Testing &
    Application starts successfully against a test database. &
    All 17 integration test cases pass; no 5xx responses from valid inputs. \\[3pt]
  System Testing &
    Application deployed locally with Docker PostgreSQL running. &
    All 8 critical system test cases pass. \\[3pt]
  Performance Testing &
    System tests passed; performance baselines established. &
    All latency metrics within the NFR thresholds defined in the SRS. \\[3pt]
  Security Testing &
    Application running with production-equivalent environment variables. &
    All 4 security test cases pass. \\
  \bottomrule
\end{longtable}

\section{Defect Classification}

\begin{longtable}{L{2cm} L{3cm} L{8cm}}
  \toprule
  \textbf{Severity} & \textbf{Label} & \textbf{Definition} \\
  \midrule
  \endhead
  1 & Critical &
    Data corruption, wrong product stored in DB, security bypass,
    system crash on valid input. Must fix before release. \\[3pt]
  2 & High &
    Feature does not work as specified (wrong score, missed hard-reject,
    broken API route). Must fix before evaluation. \\[3pt]
  3 & Medium &
    UI glitch, minor performance issue, non-critical API field missing. \\[3pt]
  4 & Low &
    Cosmetic, typo, log verbosity. Fix in next iteration. \\
  \bottomrule
\end{longtable}

% ─── CHAPTER 3: TEST ENVIRONMENT ─────────────────────────────────────────────
\chapter{Test Environment}

\section{Hardware}
\begin{itemize}[noitemsep]
  \item Development machine: Windows 11 Home Single Language 10.0.26200
  \item RAM: 8~GB minimum (Next.js + PostgreSQL + Playwright Chromium)
  \item Internet: Required for live scrape tests (VS GraphQL, Flipkart)
\end{itemize}

\section{Software}
\begin{longtable}{L{4cm} L{4cm} L{5cm}}
  \toprule
  \textbf{Component} & \textbf{Version} & \textbf{Purpose} \\
  \midrule
  \endhead
  Node.js & 20+ & Runtime for Next.js and Jest \\
  Docker Desktop & 24+ & PostgreSQL container \\
  PostgreSQL & 16 (Docker image) & Test database (separate from dev) \\
  Next.js & 16.2.4 & Application under test \\
  Jest & 29+ (to install) & Unit and integration test runner \\
  ts-jest & 29+ (to install) & TypeScript transform for Jest \\
  Playwright Test & 1.59.1 & System / E2E test runner \\
  \bottomrule
\end{longtable}

\section{Environment Variables for Testing}
\begin{verbatim}
DATABASE_URL=postgresql://aggregator:aggregator@localhost:54321/aggregator_test
GROQ_API_KEY=<mock-key-for-integration-tests>
SCRAPE_SECRET=test-secret-1234
NODE_ENV=test
\end{verbatim}

% ─── CHAPTER 4: UNIT TEST CASES ──────────────────────────────────────────────
\chapter{Unit Test Cases}

Unit tests cover pure functions in \texttt{src/lib/scrapers/matcher.ts}.
No network calls or database access are required.

\section{normalizeText()}

\rowcolors{2}{rowgray}{white}
\begin{longtable}{C{1.6cm} L{3.5cm} L{4cm} L{3.5cm} C{1.5cm}}
  \toprule
  \rowcolor{unitcol}
  \textbf{TC-ID} & \textbf{Test Name} & \textbf{Input} & \textbf{Expected Output} & \textbf{Status} \\
  \midrule
  \endhead
  \midrule
  \multicolumn{5}{r}{\small\itshape continued on next page\ldots}\\
  \endfoot
  \bottomrule
  \endlastfoot

  TC-U001 &
    Basic lowercase conversion &
    \texttt{"Apple iPhone 15"} &
    \texttt{"apple iphone 15"} &
    \PEND \\

  TC-U002 &
    Plus sign to ``plus'' &
    \texttt{"Galaxy S24+"} &
    \texttt{"galaxy s24 plus"} &
    \PEND \\

  TC-U003 &
    Model code join (letter-digit dash) &
    \texttt{"Sony WH-1000XM5"} &
    \texttt{"sony wh1000xm5"} &
    \PEND \\

  TC-U004 &
    Model code join does not affect digit-digit &
    \texttt{"Samsung 55-inch TV"} &
    \texttt{"samsung 55 inch tv"} &
    \PEND \\

  TC-U005 &
    Remaining dashes become spaces &
    \texttt{"On-Ear Headphones"} &
    \texttt{"on ear headphones"} &
    \PEND \\

  TC-U006 &
    Special characters removed &
    \texttt{"iPhone 15 (128GB)"} &
    \texttt{"iphone 15 128gb"} &
    \PEND \\

  TC-U007 &
    Multiple spaces collapsed &
    \texttt{"iPhone   15   Pro"} &
    \texttt{"iphone 15 pro"} &
    \PEND \\

  TC-U008 &
    Em-dash and underscores removed &
    \texttt{"WF--1000XM4\_v2"} &
    \texttt{"wf 1000xm4 v2"} &
    \PEND \\

\end{longtable}

\section{parseQuery()}

\rowcolors{2}{rowgray}{white}
\begin{longtable}{C{1.6cm} L{3.5cm} L{4cm} L{3.5cm} C{1.5cm}}
  \toprule
  \rowcolor{unitcol}
  \textbf{TC-ID} & \textbf{Test Name} & \textbf{Input} & \textbf{Expected Output} & \textbf{Status} \\
  \midrule
  \endhead
  \midrule
  \multicolumn{5}{r}{\small\itshape continued on next page\ldots}\\
  \endfoot
  \bottomrule
  \endlastfoot

  TC-U009 &
    Brand extraction --- Apple &
    \texttt{parseQuery("Apple iPhone 15 128GB",...)} &
    \texttt{brand: "apple"} &
    \PEND \\

  TC-U010 &
    Brand extraction --- Sony &
    \texttt{parseQuery("Sony WH-1000XM5",...)} &
    \texttt{brand: "sony"} &
    \PEND \\

  TC-U011 &
    Storage token 128GB &
    \texttt{parseQuery("iPhone 15 128GB",...)} &
    \texttt{storageToken: "128gb"} &
    \PEND \\

  TC-U012 &
    Storage token 256GB &
    \texttt{parseQuery("Galaxy S25 256GB",...)} &
    \texttt{storageToken: "256gb"} &
    \PEND \\

  TC-U013 &
    Storage token 1TB &
    \texttt{parseQuery("MacBook Pro 1TB",...)} &
    \texttt{storageToken: "1tb"} &
    \PEND \\

  TC-U014 &
    Variant --- Ultra &
    \texttt{parseQuery("Galaxy S25 Ultra",...)} &
    \texttt{variantToken: "ultra"} &
    \PEND \\

  TC-U015 &
    Variant --- Pro Max before Pro &
    \texttt{parseQuery("iPhone 15 Pro Max",...)} &
    \texttt{variantToken: "pro max"} &
    \PEND \\

  TC-U016 &
    Model token extraction &
    \texttt{parseQuery("iPhone 15 128GB",...)} &
    \texttt{modelTokens: ["15"]} &
    \PEND \\

  TC-U017 &
    Storage token excluded from model tokens &
    \texttt{parseQuery("iPhone 15 128GB",...)} &
    \texttt{modelTokens does not contain "128gb"} &
    \PEND \\

  TC-U018 &
    Model code as single token (WH-1000XM5) &
    \texttt{parseQuery("Sony WH-1000XM5",...)} &
    \texttt{modelTokens: ["wh1000xm5"]} &
    \PEND \\

  TC-U019 &
    hasRejectPhrase --- renewed query &
    \texttt{parseQuery("Renewed iPhone 14",...)} &
    \texttt{hasRejectPhrase: true} &
    \PEND \\

  TC-U020 &
    hasRejectPhrase --- normal query &
    \texttt{parseQuery("iPhone 15 128GB",...)} &
    \texttt{hasRejectPhrase: false} &
    \PEND \\

\end{longtable}

\section{scoreCandidate() --- Hard Rejects}

\rowcolors{2}{rowgray}{white}
\begin{longtable}{C{1.6cm} L{4cm} L{3.5cm} L{3.5cm} C{1.5cm}}
  \toprule
  \rowcolor{unitcol}
  \textbf{TC-ID} & \textbf{Test Name} & \textbf{Candidate Title} & \textbf{Expected Result} & \textbf{Status} \\
  \midrule
  \endhead
  \midrule
  \multicolumn{5}{r}{\small\itshape continued on next page\ldots}\\
  \endfoot
  \bottomrule
  \endlastfoot

  TC-U021 &
    Reject accessory (case) &
    \texttt{"iPhone 15 128GB Case"} &
    \texttt{accepted: false, score: -100} &
    \PEND \\

  TC-U022 &
    Reject accessory (charger) &
    \texttt{"20W USB-C Charger for iPhone"} &
    \texttt{accepted: false, score: -100} &
    \PEND \\

  TC-U023 &
    Reject accessory (tempered glass) &
    \texttt{"Tempered Glass for Samsung S24"} &
    \texttt{accepted: false, score: -100} &
    \PEND \\

  TC-U024 &
    Reject renewed (not requested) &
    \texttt{"Renewed iPhone 15 128GB"} &
    query hasRejectPhrase=false $\Rightarrow$
    \texttt{accepted: false, score: -80} &
    \PEND \\

  TC-U025 &
    Allow renewed (query requests it) &
    \texttt{"Renewed iPhone 15 128GB"} &
    query hasRejectPhrase=true $\Rightarrow$
    \texttt{accepted: true} &
    \PEND \\

  TC-U026 &
    Reject zero model token match &
    \texttt{"Apple iPhone 14 128GB"} &
    query modelTokens=["15"] $\Rightarrow$
    \texttt{accepted: false, score: -50} &
    \PEND \\

  TC-U027 &
    Reject storage conflict (256GB vs 128GB) &
    \texttt{"Apple iPhone 15 256GB"} &
    query storageToken="128gb" $\Rightarrow$
    \texttt{accepted: false, score: -60} &
    \PEND \\

  TC-U028 &
    Reject variant conflict (Pro vs Ultra) &
    \texttt{"Samsung Galaxy S25 Pro 256GB"} &
    query variantToken="ultra" $\Rightarrow$
    \texttt{accepted: false, score: -60} &
    \PEND \\

\end{longtable}

\section{scoreCandidate() --- Soft Scores}

\rowcolors{2}{rowgray}{white}
\begin{longtable}{C{1.6cm} L{4cm} L{3.5cm} L{3.5cm} C{1.5cm}}
  \toprule
  \rowcolor{unitcol}
  \textbf{TC-ID} & \textbf{Test Name} & \textbf{Candidate Title} & \textbf{Expected Result} & \textbf{Status} \\
  \midrule
  \endhead
  \midrule
  \multicolumn{5}{r}{\small\itshape continued on next page\ldots}\\
  \endfoot
  \bottomrule
  \endlastfoot

  TC-U029 &
    Brand match earns +30 &
    \texttt{"Apple iPhone 15 128GB"} &
    brand "apple" present $\Rightarrow$ score includes +30 &
    \PEND \\

  TC-U030 &
    Missing brand deducts -30 &
    \texttt{"Generic Phone 15 128GB"} &
    query brand="apple" $\Rightarrow$ score includes -30 &
    \PEND \\

  TC-U031 &
    All model tokens matched --- +40 &
    \texttt{"iPhone 15 128GB"} &
    modelTokens=["15"] fully matched $\Rightarrow$ +40 &
    \PEND \\

  TC-U032 &
    Partial model token match (half) &
    \texttt{"Galaxy S24 256GB"} &
    modelTokens=["s24","256gb"] (1/2 matched) $\Rightarrow$ +20 &
    \PEND \\

  TC-U033 &
    Storage match +20 &
    \texttt{"iPhone 15 128GB"} &
    storageToken="128gb" matched $\Rightarrow$ +20 &
    \PEND \\

  TC-U034 &
    No storage in title -5 &
    \texttt{"iPhone 15 Midnight"} &
    storageToken="128gb", no GB in title $\Rightarrow$ -5 &
    \PEND \\

  TC-U035 &
    Variant match +20 &
    \texttt{"Galaxy S25 Ultra 256GB"} &
    variantToken="ultra" matched $\Rightarrow$ +20 &
    \PEND \\

  TC-U036 &
    Unexpected variant -15 &
    \texttt{"Galaxy S25 Ultra 256GB"} &
    query no variantToken $\Rightarrow$ -15 &
    \PEND \\

  TC-U037 &
    Combo/bundle penalty -30 &
    \texttt{"iPhone 15 128GB + AirPods Bundle"} &
    query no bundle keyword $\Rightarrow$ -30 &
    \PEND \\

  TC-U038 &
    TV title with ``4K Ultra HD'' --- no variant penalty &
    \texttt{"Samsung 55 inch 4K Ultra HD Smart TV"} &
    query no variantToken $\Rightarrow$ ``ultra hd'' stripped before
    detection; no -15 penalty &
    \PEND \\

  TC-U039 &
    Full iPhone 15 128GB positive score &
    \texttt{"Apple iPhone 15 128GB Blue"} &
    query "Apple iPhone 15 128GB" $\Rightarrow$
    score $\geq$ 80, accepted: true &
    \PEND \\

  TC-U040 &
    Vague query accepted at lower threshold &
    \texttt{"Sony WH-1000XM5 Headphones"} &
    query "Sony headphones", modelTokens=[] $\Rightarrow$
    threshold=20, accepted: true &
    \PEND \\

\end{longtable}

% ─── CHAPTER 5: INTEGRATION TEST CASES ──────────────────────────────────────
\chapter{Integration Test Cases}

Integration tests exercise the Next.js API route handlers against a real
(test) PostgreSQL database. External scrapers are mocked to return fixture data.

\section{POST /api/search/live}

\rowcolors{2}{rowgray}{white}
\begin{longtable}{C{1.6cm} L{3.5cm} L{3.5cm} L{3.5cm} C{1.5cm}}
  \toprule
  \rowcolor{intcol}
  \textbf{TC-ID} & \textbf{Test Name} & \textbf{Input / Precondition} & \textbf{Expected Result} & \textbf{Status} \\
  \midrule
  \endhead
  \midrule
  \multicolumn{5}{r}{\small\itshape continued on next page\ldots}\\
  \endfoot
  \bottomrule
  \endlastfoot

  TC-I001 &
    Valid query returns 200 with productId &
    Body: \texttt{\{"query":"iPhone 15 128GB"\}} &
    HTTP 200; response body contains \texttt{productId} (integer) &
    \PEND \\

  TC-I002 &
    Missing query returns 400 &
    Body: \texttt{\{\}} &
    HTTP 400; body contains \texttt{\{"error":"Query is required"\}} &
    \PEND \\

  TC-I003 &
    Empty query string returns 400 &
    Body: \texttt{\{"query":""\}} &
    HTTP 400 &
    \PEND \\

  TC-I004 &
    Product record created in DB &
    First time querying "iPhone 15 128GB" &
    \texttt{Product} with slug \texttt{iphone-15-128gb} created in DB &
    \PEND \\

  TC-I005 &
    ProductListing created per scraper result &
    Mock returns VS + FK results &
    Two \texttt{ProductListing} rows with source vijaysales and flipkart &
    \PEND \\

  TC-I006 &
    PriceHistory row appended &
    Fixture product price = 58190 &
    One \texttt{PriceHistory} row per listing with correct price &
    \PEND \\

  TC-I007 &
    Second call upserts, not duplicates &
    Same query called twice &
    DB still has one \texttt{Product} row; listing price updated &
    \PEND \\

  TC-I008 &
    Response includes AI analysis &
    Groq mock returns \texttt{\{summary,recommendation,...\}} &
    Response body contains \texttt{aiAnalysis.summary} (non-empty string) &
    \PEND \\

  TC-I009 &
    AI failure does not block response &
    Groq mock throws network error &
    HTTP 200 still returned; \texttt{aiAnalysis} may be null &
    \PEND \\

\end{longtable}

\section{GET /api/search}

\rowcolors{2}{rowgray}{white}
\begin{longtable}{C{1.6cm} L{3.5cm} L{3.5cm} L{3.5cm} C{1.5cm}}
  \toprule
  \rowcolor{intcol}
  \textbf{TC-ID} & \textbf{Test Name} & \textbf{Query Params} & \textbf{Expected Result} & \textbf{Status} \\
  \midrule
  \endhead
  \midrule
  \multicolumn{5}{r}{\small\itshape continued on next page\ldots}\\
  \endfoot
  \bottomrule
  \endlastfoot

  TC-I010 &
    Full-text search by name &
    \texttt{?q=iphone} &
    Returns products where name contains "iphone" (case-insensitive) &
    \PEND \\

  TC-I011 &
    Category filter &
    \texttt{?category=Smartphones} &
    All returned products have category = "Smartphones" &
    \PEND \\

  TC-I012 &
    Sort by price ascending &
    \texttt{?sort=price\_asc} &
    Products ordered by minimum listing price ascending &
    \PEND \\

  TC-I013 &
    Sort by rating descending &
    \texttt{?sort=rating} &
    Products ordered by average rating descending &
    \PEND \\

  TC-I014 &
    No results for unknown query &
    \texttt{?q=xyznoproduct999} &
    HTTP 200; \texttt{data: []} &
    \PEND \\

\end{longtable}

\section{POST /api/ai/analyze}

\rowcolors{2}{rowgray}{white}
\begin{longtable}{C{1.6cm} L{4cm} L{4cm} L{3.5cm} C{1.5cm}}
  \toprule
  \rowcolor{intcol}
  \textbf{TC-ID} & \textbf{Test Name} & \textbf{Input / Precondition} & \textbf{Expected Result} & \textbf{Status} \\
  \midrule
  \endhead
  \bottomrule
  \endlastfoot

  TC-I015 &
    Returns AI analysis for valid product &
    Existing productId, no cached analysis &
    HTTP 200; body contains \texttt{summary}, \texttt{recommendation},
    \texttt{bestSource} &
    \PEND \\

  TC-I016 &
    Cached result returned within 24h &
    Product has AIAnalysis row $<$ 24h old &
    HTTP 200; body contains \texttt{cached: true} &
    \PEND \\

  TC-I017 &
    Refreshes after 24h cache expiry &
    AIAnalysis row $>$ 24h old &
    Groq is called; new analysis stored; \texttt{cached: false} &
    \PEND \\

\end{longtable}

\section{POST /api/scrape}

\rowcolors{2}{rowgray}{white}
\begin{longtable}{C{1.6cm} L{4cm} L{4cm} L{3.5cm} C{1.5cm}}
  \toprule
  \rowcolor{intcol}
  \textbf{TC-ID} & \textbf{Test Name} & \textbf{Input / Precondition} & \textbf{Expected Result} & \textbf{Status} \\
  \midrule
  \endhead
  \bottomrule
  \endlastfoot

  TC-I018 &
    Missing secret rejected &
    No \texttt{x-scrape-secret} header &
    HTTP 403 Forbidden &
    \PEND \\

  TC-I019 &
    Wrong secret rejected &
    Header: \texttt{x-scrape-secret: wrongvalue} &
    HTTP 403 Forbidden &
    \PEND \\

  TC-I020 &
    Correct secret triggers scrapers &
    Header: correct SCRAPE\_SECRET; scrapers mocked &
    HTTP 200; response contains \texttt{upserted} count $\geq 1$ &
    \PEND \\

\end{longtable}

\section{GET /api/price-history/[id]}

\rowcolors{2}{rowgray}{white}
\begin{longtable}{C{1.6cm} L{4cm} L{4cm} L{3.5cm} C{1.5cm}}
  \toprule
  \rowcolor{intcol}
  \textbf{TC-ID} & \textbf{Test Name} & \textbf{Input} & \textbf{Expected Result} & \textbf{Status} \\
  \midrule
  \endhead
  \bottomrule
  \endlastfoot

  TC-I021 &
    Returns price history for known product &
    Valid productId with 3 history rows &
    HTTP 200; array of 3 objects with \texttt{price}, \texttt{recordedAt}, \texttt{source} &
    \PEND \\

  TC-I022 &
    Returns empty array for product with no history &
    Valid productId, no PriceHistory rows &
    HTTP 200; \texttt{data: []} &
    \PEND \\

  TC-I023 &
    Invalid productId returns 404 &
    Non-existent id (e.g., 999999) &
    HTTP 404 &
    \PEND \\

\end{longtable}

% ─── CHAPTER 6: SYSTEM TEST CASES ────────────────────────────────────────────
\chapter{System / End-to-End Test Cases}

System tests validate complete user workflows in a running application.
Tests are performed manually unless otherwise noted.

\rowcolors{2}{rowgray}{white}
\begin{longtable}{C{1.6cm} L{3.5cm} L{4cm} L{3.5cm} C{1.5cm}}
  \toprule
  \rowcolor{syscol}
  \textbf{TC-ID} & \textbf{Test Name} & \textbf{Steps} & \textbf{Expected Result} & \textbf{Status} \\
  \midrule
  \endhead
  \midrule
  \multicolumn{5}{r}{\small\itshape continued on next page\ldots}\\
  \endfoot
  \bottomrule
  \endlastfoot

  TC-S001 &
    Home page loads correctly &
    Navigate to \texttt{http://localhost:3000/} &
    Hero section visible with search bar; dark theme applied; no console errors &
    \PEND \\

  TC-S002 &
    Search for existing product --- cache hit &
    Database seeded; enter "iPhone 15" in search bar; press Enter &
    Results page shows at least one product card with correct name, price, and
    platform badge; response within 500~ms &
    \PEND \\

  TC-S003 &
    Search for unknown product triggers live search &
    Database empty; enter "Sony WH-1000XM5" in search bar &
    LiveSearchTrigger appears with animated platform steps (Amazon, Flipkart,
    Vijay Sales); after completion, redirects to product page &
    \PEND \\

  TC-S004 &
    Live search animated steps display correctly &
    While live search is running (observe UI) &
    Each platform shows: ``Searching\ldots'' $\to$ ``Found it!'' (or skipped with
    amber warning); steps do not skip prematurely &
    \PEND \\

  TC-S005 &
    Product page shows price comparison &
    Navigate to \texttt{/product/\{id\}} for a product with VS + FK listings &
    Price Comparison tab shows two listing cards; cheapest marked ``Best Deal'';
    price difference percentage visible on the other card &
    \PEND \\

  TC-S006 &
    AI Analysis tab renders recommendation &
    Click ``AI Analysis'' tab on product page &
    Loading skeleton visible briefly; then summary, recommendation, and
    bestSource badge appear; no console errors &
    \PEND \\

  TC-S007 &
    Price history chart renders &
    Product page with at least 2 price history rows &
    Line chart visible on product page below listing cards;
    axes labelled with dates and INR values &
    \PEND \\

  TC-S008 &
    Category filter narrows results &
    Search results page with mixed categories; select ``Smartphones'' filter &
    Only Smartphone products shown; count decreases or stays equal &
    \PEND \\

  TC-S009 &
    Sort by price ascending &
    Search results page; select ``Price: Low to High'' sort &
    Products displayed in ascending price order; verified by comparing first
    and last card prices &
    \PEND \\

  TC-S010 &
    Dashboard KPI cards load &
    Navigate to \texttt{/dashboard} with seeded data &
    KPI cards show non-zero values for total products, listings, and searches;
    pie and bar charts render without errors &
    \PEND \\

  TC-S011 &
    Refresh Prices button re-triggers live scrape &
    On product page, click ``Refresh Prices'' &
    Toast notification ``Refreshing\ldots'' appears; on completion, toast says
    success; PriceHistory row count increases by at least 1 in DB &
    \PEND \\

  TC-S012 &
    Dark mode persists across navigation &
    Open app in dark mode; navigate from home $\to$ search $\to$ product $\to$ dashboard &
    Dark theme maintained on all pages; no flash of light theme &
    \PEND \\

\end{longtable}

% ─── CHAPTER 7: PERFORMANCE TEST CASES ───────────────────────────────────────
\chapter{Performance Test Cases}

Performance tests validate that the system meets the NFRs defined in the SRS.

\rowcolors{2}{rowgray}{white}
\begin{longtable}{C{1.6cm} L{3.5cm} L{3.5cm} L{3.5cm} C{1.5cm}}
  \toprule
  \rowcolor{perfcol}
  \textbf{TC-ID} & \textbf{Test Name} & \textbf{Method / Tool} & \textbf{Acceptance Criterion} & \textbf{Status} \\
  \midrule
  \endhead
  \midrule
  \multicolumn{5}{r}{\small\itshape continued on next page\ldots}\\
  \endfoot
  \bottomrule
  \endlastfoot

  TC-P001 &
    Live search total latency (all 3 platforms) &
    Measure wall-clock time from POST \texttt{/api/search/live} to response;
    repeat 3 times; take median &
    Median $\leq$ 60 seconds on a 20~Mbps connection &
    \PEND \\

  TC-P002 &
    Cached database search latency &
    GET \texttt{/api/search?q=iphone} against seeded DB;
    measure response time with browser DevTools Network tab &
    Response time $\leq$ 500~ms; TTFB $\leq$ 200~ms &
    \PEND \\

  TC-P003 &
    Product page SSR latency &
    Navigate to \texttt{/product/\{id\}} (populated product);
    measure TTFB via DevTools &
    TTFB $\leq$ 2 seconds &
    \PEND \\

  TC-P004 &
    AI analysis latency (Groq API) &
    POST \texttt{/api/ai/analyze} with a product having 3 listings;
    measure from request to JSON response &
    Response time $\leq$ 8 seconds &
    \PEND \\

  TC-P005 &
    AI analysis cache hit latency &
    POST \texttt{/api/ai/analyze} for a product with cached analysis ($<$ 24h) &
    Response time $\leq$ 100~ms (DB-only, no Groq call) &
    \PEND \\

  TC-P006 &
    Vijay Sales scraper latency &
    Measure \texttt{liveVS()} execution time for one product query (3 runs, median) &
    $\leq$ 3 seconds including GraphQL request + scoring &
    \PEND \\

  TC-P007 &
    Flipkart Playwright scraper latency &
    Measure \texttt{liveFlipkart()} execution time for one query &
    $\leq$ 45 seconds (includes browser launch, page load, DOM evaluation) &
    \PEND \\

  TC-P008 &
    5 concurrent live search requests &
    Use \texttt{k6} to simulate 5 virtual users simultaneously sending
    POST \texttt{/api/search/live} with different queries &
    All 5 requests complete with HTTP 200; no 5xx errors; no deadlocks &
    \PEND \\

\end{longtable}

% ─── CHAPTER 8: SECURITY TEST CASES ─────────────────────────────────────────
\chapter{Security Test Cases}

\rowcolors{2}{rowgray}{white}
\begin{longtable}{C{1.6cm} L{3.5cm} L{3.5cm} L{3.5cm} C{1.5cm}}
  \toprule
  \rowcolor{seccol}
  \textbf{TC-ID} & \textbf{Test Name} & \textbf{Method} & \textbf{Expected Result} & \textbf{Status} \\
  \midrule
  \endhead
  \bottomrule
  \endlastfoot

  TC-SEC001 &
    Scrape endpoint --- missing secret &
    POST \texttt{/api/scrape} with no \texttt{x-scrape-secret} header &
    HTTP 403; body: \texttt{\{"error":"Unauthorized"\}}; no scrape triggered &
    \PEND \\

  TC-SEC002 &
    Scrape endpoint --- wrong secret &
    POST \texttt{/api/scrape} with header value \texttt{"wrongsecret"} &
    HTTP 403; body: \texttt{\{"error":"Unauthorized"\}} &
    \PEND \\

  TC-SEC003 &
    SQL injection in search query &
    GET \texttt{/api/search?q=' OR '1'='1} &
    HTTP 200 with valid (possibly empty) results; no DB error; Prisma
    parameterisation prevents injection &
    \PEND \\

  TC-SEC004 &
    No env variable leakage in response &
    Inspect all API response bodies for strings containing
    \texttt{DATABASE\_URL}, \texttt{GROQ\_API\_KEY}, or \texttt{SCRAPE\_SECRET} &
    No API response contains environment variable values &
    \PEND \\

  TC-SEC005 &
    No stack trace in error response &
    Send malformed JSON to \texttt{/api/ai/analyze} &
    HTTP 4xx/5xx; response body contains only a user-facing error message,
    not a Node.js stack trace &
    \PEND \\

  TC-SEC006 &
    HTTPS enforced in production &
    Attempt HTTP request to the production URL (if deployed) &
    Redirected to HTTPS or connection refused; no plaintext communication &
    \PEND \\

\end{longtable}

% ─── CHAPTER 9: TRACEABILITY MATRIX ─────────────────────────────────────────
\chapter{Requirements Traceability Matrix}

The table below maps each functional requirement from the SRS to the test
cases that verify it.

\rowcolors{2}{rowgray}{white}
\begin{longtable}{L{2cm} L{5.5cm} L{6cm}}
  \toprule
  \textbf{FR-ID} & \textbf{Requirement Name} & \textbf{Covering Test Cases} \\
  \midrule
  \endhead
  \midrule
  \multicolumn{3}{r}{\small\itshape continued on next page\ldots}\\
  \endfoot
  \bottomrule
  \endlastfoot

  FR-001 & Live Search &
    TC-I001, TC-I002, TC-I003, TC-I004, TC-I005, TC-I006, TC-I007,
    TC-S003, TC-S004, TC-P001 \\[3pt]

  FR-002 & Product Identity Matching &
    TC-U001--TC-U040 (all unit tests cover the scoring engine);
    TC-I004, TC-I005 (verify correct product stored) \\[3pt]

  FR-003 & Price Comparison Display &
    TC-S005, TC-S009, TC-I010, TC-I011, TC-I012 \\[3pt]

  FR-004 & AI Purchase Recommendation &
    TC-I008, TC-I009, TC-I015, TC-I016, TC-I017, TC-S006, TC-P004, TC-P005 \\[3pt]

  FR-005 & Price History Tracking &
    TC-I006, TC-S007, TC-I021, TC-I022, TC-P002 \\[3pt]

  FR-006 & Batch Scraping &
    TC-I018, TC-I019, TC-I020 \\[3pt]

  FR-007 & Database Text Search and Filtering &
    TC-I010, TC-I011, TC-I012, TC-I013, TC-I014, TC-S002, TC-S008 \\[3pt]

  FR-008 & On-Demand Price Refresh &
    TC-S011, TC-P006, TC-P007 \\[3pt]

  FR-009 & Administrative Dashboard &
    TC-S010 \\[3pt]

  FR-010 & Dark Mode UI Theme &
    TC-S001, TC-S012 \\[3pt]

  NFR-P01 & Live search $\leq$ 60s &
    TC-P001 \\[3pt]

  NFR-P02 & Cached search $\leq$ 500ms &
    TC-P002 \\[3pt]

  NFR-P03 & Product page TTFB $\leq$ 2s &
    TC-P003 \\[3pt]

  NFR-P04 & AI latency $\leq$ 8s &
    TC-P004 \\[3pt]

  NFR-P05 & 5 concurrent users &
    TC-P008 \\[3pt]

  NFR-R01 & Partial scrape failure graceful &
    TC-I009 \\[3pt]

  NFR-S01 & Scrape endpoint protection &
    TC-SEC001, TC-SEC002 \\[3pt]

  NFR-S03 & Input sanitisation &
    TC-SEC003 \\[3pt]

  NFR-S04 & No sensitive data in responses &
    TC-SEC004, TC-SEC005 \\[3pt]

\end{longtable}

% ─── CHAPTER 10: TEST SUMMARY ────────────────────────────────────────────────
\chapter{Test Summary}

\section{Test Case Count by Category}

\begin{longtable}{L{4cm} C{2cm} C{3cm} C{3cm}}
  \toprule
  \textbf{Category} & \textbf{Count} & \textbf{Automated?} & \textbf{Priority} \\
  \midrule
  \endhead
  \bottomrule
  \endlastfoot

  Unit Tests (\texttt{matcher.ts}) & 40 & Yes (Jest) & Critical \\
  Integration Tests (API routes)   & 23 & Yes (Jest + Supertest) & High \\
  System / E2E Tests               & 12 & Manual / Playwright & High \\
  Performance Tests                & 8  & Manual / k6 & Medium \\
  Security Tests                   & 6  & Manual / OWASP ZAP & High \\
  \midrule
  \textbf{Total} & \textbf{89} & & \\
  \bottomrule
\end{longtable}

\section{Known Limitations and Risks}

\begin{enumerate}[noitemsep]
  \item \textbf{Amazon Bot Detection (Critical Risk):} Amazon.in returns HTTP 503
        for programmatic requests. TC-I005 and TC-S003 will show Amazon results
        as null in all real test runs. This is a fundamental platform constraint,
        not a system defect.

  \item \textbf{Playwright Fragility (Medium Risk):} Flipkart's DOM structure
        may change between evaluation periods, causing TC-P007 and related
        Flipkart tests to fail. The scraper would need a DOM selector update.

  \item \textbf{Groq API Quota (Low Risk):} Integration tests that call the
        real Groq API will consume token quota. A mock should be used in CI
        environments.

  \item \textbf{No Automated Test Suite Currently Configured (High Risk):}
        All 89 test cases are in \textit{Planned} status. Configuring Jest and
        ts-jest is the highest-priority outstanding task before test execution.
\end{enumerate}

\section{Recommended Test Execution Order}
\begin{enumerate}[noitemsep]
  \item Configure Jest + ts-jest in the project.
  \item Run all unit tests (TC-U001--TC-U040) --- no infrastructure required.
  \item Start Docker PostgreSQL test instance.
  \item Run integration tests (TC-I001--TC-I023) with mocked scrapers.
  \item Start full application; run system tests manually (TC-S001--TC-S012).
  \item Run performance tests (TC-P001--TC-P008) individually.
  \item Run security tests (TC-SEC001--TC-SEC006).
\end{enumerate}

\chapter*{Revision History}
\begin{longtable}{C{1.5cm} C{2cm} L{4cm} L{5cm}}
  \toprule
  \textbf{Version} & \textbf{Date} & \textbf{Author} & \textbf{Changes} \\
  \midrule
  \endhead
  \bottomrule
  \endlastfoot
  1.0 & April 2026 & Adrij Bhadra &
    Initial release. 89 test cases across 5 categories. Full traceability
    matrix. Known limitations documented. \\
  \bottomrule
\end{longtable}

\end{document}
